%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Honors \& Awards}


\begin{cvhonors}

%---------------------------------------------------------

    \cvhonor
    {2023}
    {James Mill Peirce Fellowship}{Harvard University}
    {Cambridge, MA}
    {The James Mill Peirce Fellowship recognizes excellent graduate students in the natural sciences, mathematics, and engineering at the Harvard Graduate School of Arts and Sciences.}

    \cvhonor
    {2023}
    {Graduate Research Fellowship}{National Science Foundation}
    {Cambridge, MA}
    {The NSF GRFP recognizes and supports outstanding graduate students in science, technology, engineering, and mathematics. Awarded for work on machine learning and causal inference.}

    \cvhonor
    {2021}
    {Rhodes Scholarship}{Rhodes Trust}
    {Oxford, UK}
    {The Rhodes Scholarship is a postgraduate award for students to study at the University of Oxford.}

    \cvhonor
    {2021}
    {Outstanding Senior Thesis Award and Firestone Medal}{Stanford University}
    {Stanford, CA}
    {Best thesis award in sociology and medal for top Stanford-wide theses. Received for work on the history of trial avoidance mechanisms and how colonialism and imperialism drove their diffusion.}

    \cvhonor
    {2020}
    {Spotlight Talk}{Computational Biology Workshop, ICML}
    {Vienna, AT}
    {Exceptional submissions to the workshop are invited to give a presentation on their work.}

    \cvhonor
    {2017}
    {G.R.E.A.T. Award}{NHGRI, National Institutes of Health}
    {Bethesda, MD}
    {Genome Recognition of Employee Accomplishments and Talents, for work in the Ostrander Lab.}

\end{cvhonors}
