%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Presentations}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvhonors}

%---------------------------------------------------------
    \cvhonor
    {2025} % Date(s)
    {Generative modeling on the space of empirical measures} % Role
    {Boston Diffusion Day} % Event
    {Cambridge, MA} % Location

    \cvhonor
    {2025} % Date(s)
    {Generative modeling on the space of empirical measures} % Role
    {Harvard Statistics Seminar} % Event
    {Cambridge, MA} % Location
    {Outlining the history of the field of fair machine learning and arguing that ``theoretical fairness'' is a doomed project.}
    
    \cvhonor
    {2025} % Date(s)
    {False Promises and False Premises of Fair Machine Learning} % Role
    {Columbia Algorithms and Society Seminar} % Event
    {New York, NY} % Location
    {Outlining the history of the field of fair machine learning and arguing that ``theoretical fairness'' is a doomed project.}
    
    \cvhonor
    {2025} % Date(s)
    {Predicting perturbations at single-cell resolution} % Role
    {Cell Circuits and Epigenomics Seminar} % Event
    {Cambridge, MA} % Location
    {An overview of the problem of single-cell perturbation prediction, presentation of results from benchmarking existing methods, and our novel approach for \textit{in silico} experimentation.}

    \cvhonor
    {2023} % Date(s)
    {Constrained Riemannian Diffusion Modeling} % Role
    {Thesis Defense} % Event
    {Oxford, UK} % Location

    \cvhonorstub
    {2022} % Date(s)
    {Invited talk, Should attention be all we need?} % Role
    {Stanford Human Centered Artificial Intelligence} % Event
    {Stanford, CA} % Location
    

    \cvhonorstub
    {2022} % Date(s)
    {Invited talk, Should attention be all we need?} % Role
    {DeepMind Sociotechnical Systems} % Event
    {London, England} % Location
    

    \cvhonor
    {2022} % Date(s)
    {Conference talk} % Role
    {Law and Society Association Annual Meeting} % Event
    {Lisbon, Portugal} % Location
    {On `Making (Global) Criminal Procedure'. Outlining the history of two trial avoidance mechanisms, plea bargaining and penal orders, and how colonialism and imperialism drove their diffusion.}
    
    \cvhonor
    {2021} % Date(s)
    {Conference talk} % Role
    {American Political Science Association Annual Meeting} % Event
    {Seattle, WA} % Location
    {Developed sparse-covariance Gaussian Mixture Models for studying political belief networks and the connections to Brandom's inferentialist account of belief formation. With J. Green and N. T. Davis.}


%---------------------------------------------------------
\end{cvhonors}
