%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}
\begin{cvparagraph}

\honorpositionstyle{Published Papers}

\begin{addmargin}[2em]{0em}

Alexander C Furnas, \textbf{Nic Fishman}, Leah Rosenstiel, and Dashun Wang, 2025. Partisan disparities in the funding of science in the United States. \textit{Science}.

\textbf{Nic Fishman} and Evan Rosenman, 2024. Estimating Vote Choice in US Elections with Approximate Poisson-Binomial Logistic Regression. \textit{OPT 2024}.

Jake Fawkes, \textbf{Nic Fishman}, Mel Andrews, and Zachary Lipton, 2024. The fragility of fairness: Causal sensitivity analysis for fair machine learning. \textit{Advances in Neural Information Processing Systems}.

Hamed Nilforoshan, Wenli Looi, Emma Pierson, Blanca Villanueva, \textbf{Nic Fishman}, Yiling Chen, John Sholar, Beth Redbird, David Grusky, and Jure Leskovec, 2023. Human mobility networks reveal increased segregation in large cities. \textit{Nature}.

\textbf{Nic Fishman}, Leo Klarner, Valentin De Bortoli, Emile Mathieu, and Michael Hutchinson, 2023. Diffusion models for constrained domains. \textit{Transactions on Machine Learning Research}.

\textbf{Nic Fishman}, Leo Klarner, Emile Mathieu, Michael Hutchinson, and Valentin De Bortoli, 2023. Metropolis sampling for constrained diffusion models. \textit{Advances in Neural Information Processing Systems}.

\textbf{Nic Fishman} and Nicholas T Davis, 2022. Change we can believe in: Structural and content dynamics within belief networks. \textit{American Journal of Political Science}.

\textbf{Nic Fishman} and Leif Hancox-Li, 2022. Should attention be all we need? The epistemic and ethical implications of unification in machine learning. \textit{Proceedings of the 2022 ACM Conference on Fairness, Accountability,}.

\textbf{Fishman}, N., Shrikumar, A., Marinov, G., Kundaje, and A., . Systematic characterization of generative models for de novo design of regulatory DNA. \textit{(Spotlight) International Conference on Machine Learning, Computational Biology Workshop, 2020}.

\end{addmargin}

\honorpositionstyle{Working Papers}

\begin{addmargin}[2em]{0em}

\textbf{Nic Fishman}, Gokul Gowri, Peng Yin, Jonathan Gootenberg, and Omar Abudayyeh, 2025. Generative Distribution Embeddings. \textit{arXiv preprint arXiv:2505.18150}.

\textbf{Nic Fishman}, 2021. Making (Global) Criminal Procedure: Empire, the End of Justice, and the Rise of Efficiency. \textit{Stanford University}.

Ben-Menachem, J., \textbf{* Fishman}, N., * Galper, and G.*, . The False Promise of Controlling False Positives: Ephemerality and the "Replication Crisis" in Observational Studies.

\textbf{Fishman} and N., . Principled Models for Analyzing Max-Diff Surveys.

\end{addmargin}

\end{cvparagraph}
